Full Brain BOLD Signal Parameter Estimation \\ using Particle Filters

### 2010-08-27 doc/presentation/main.tex
needs fixes....but whateve
some comments
changed the section on bold, need to change the particle filter now

\section{Introduction}
%2
\begin{frame}{Balloon Model}
\begin{figure}
\includegraphics[width=10cm]{model}
\caption{
    \tiny
    \cite{Riera2003}
}
\end{figure}
\note{Rates from below 1 Hz to 5 to 6 Hundred Hz}
\note{Change in average firing rates increase metabolism and sympathetic response causes
        increased inflow of oxygenated blood.}
\note{In the version of the Balloon model I used, the flow is locked to metabolism.}
\note{According the balloon model this increases the local blood volume, and the outflow pressure.}
\note{So the signal is altered by changes in the ratio of Deoxyhemoglobin and Oxygenated Hemoglobin,
        which are a function of Volume and Oxygenation.}
\end{frame}

%4
\begin{frame}{Time Changing Parameters}
    \includegraphics[clip=true,trim=3cm 1cm 3cm 1cm,width=\textwidth]{stateTS}
    \note{Should include a picture of the different parts of the BOLD signal}
\end{frame}

%6 
\begin{frame}{BOLD State Equations}
  \small
  \begin{itemize}
    \item Flow Inducing Signal
    $$\dot{s}(t) = \epsilon u(t) - s(t)/\tau_s - (f(t)-1)/\tau_f$$
    \item Normalized Cerebral Blood Inflow:
    $$\dot{f}(t) = s $$
    \item Normalized Cerebral Blood Volume:
    $$\dot{v}(t) = (1/\tau_0)( f(t) - v(t) ^ {1/\alpha}) $$
    \item Normalized Deoxyhaemoglobin Content:\\
    $$\dot{q}(t) = \frac{1}{\tau_0}\left(\frac{f(t)(1-(1-E_0)^{1/f(t)})}{E_0} -
            \frac{q(t)}{v(t)^{1-1/\alpha}}\right)$$
    \item Hemodynamic Response - BOLD Signal
    $$y(t) = V_0(a_1( 1 - Q(t)) - a_2(1 - V(t)))$$
  \end{itemize}
  \note{System is dissipative:}
  \note{If no input is provided, it will rather quickly decay.}
  \note{Constant input leads to steady state response.}
  \note{First term in $\dot{q}$ is the metabolism term.}
  \note{Outflow is the $v^{1/\alpha}$ term}
  \note{Significant nonlinearity.}
\end{frame}

@@

\section{Particle Filter}
\begin{frame}{Construction}
\begin{itemize}
    \item Initialize Particles with Prior ($\alpha$):\\
        $$\{(x^i_0,w^i) : x^i_0 \sim \alpha(X), w^i = 
                \frac{1}{N_p}, i \in \{1, 2, ... , N_p\} \}$$
        $$\alpha(X) \stackrel{\text{\tiny{k=0}}}{\approx} P(x_k) 
                = \sum_{i=0}^{N_p} w^i\delta(x_k - x^i_k ) dx$$
    \item Particle Weights at time $t_k$:\\
        $$w^i_k \propto \frac{P(x^i_{0:k} | y_{0:k})}{q(x^i_{0:k} | y_{0:k})}$$
      \note{$q$ is the density/location of the particle}
      \note{$p$ is the actual probability }
    \item Adding Measurements:\\
        $$w^i_k \propto & w^i_{k-1}P(y_k| x_k) $$
      \note{Because of the proportion, note that the weights do not
            have to integrate to 1, and can be extremely large or extremely small}
\end{itemize}
\end{frame}

>>>>

\section{Introduction}
\begin{frame}{Balloon Model}
\begin{figure}
\includegraphics[width=10cm]{model}
\caption{
    \tiny
    \cite{Riera2003}
}
\end{figure}
\note{Rates from below 1 Hz to 5 to 6 Hundred Hz}
\note{Change in average firing rates increase metabolism and sympathetic response causes
        increased inflow of oxygenated blood.}
\note{In the version of the Balloon model I used, the flow is locked to metabolism.}
\note{According the balloon model this increases the local blood volume, and the outflow pressure.}
\note{So the signal is altered by changes in the ratio of Deoxyhemoglobin and Oxygenated Hemoglobin,
        which are a function of Volume and Oxygenation.}
\end{frame}

\begin{frame}{Time Changing Parameters}
\begin{figure}
    \includegraphics[width=\textwidth]{graphs}
\caption{
    \tiny
    \cite{Buxton2004}
}
\end{figure}
\end{frame}

%more expansion of all the parameters
\begin{frame}{BOLD State Space Model}
  \scriptsize
  \begin{columns}
  \begin{column}{.7\textwidth}
    \begin{itemize}
    \item State Vector:
    \begin{eqnarray}
    \dot{s}(t) &=& \epsilon u(t) - s(t)/\tau_s - (f(t)-1)/\tau_f \nonumber \\
    \dot{f}(t) &=& s \nonumber \\
    \dot{v}(t) &=& (1/\tau_0)( f(t) - v(t) ^ {1/\alpha}) \nonumber \\
    \dot{q}(t) &=& \frac{1}{\tau_0}\left(\frac{f(t)(1-(1-E_0)^{1/f(t)})}{E_0} -
            \frac{q(t)}{v(t)^{1-1/\alpha}}\right) \nonumber 
    \end{eqnarray}
    \item Output:
    $$y(t) = V_0(a_1( 1 - Q(t)) - a_2(1 - V(t)))$$
    \end{itemize}
  \end{column}

  \begin{column}{.3\textwidth}
        State Variables:
        $$s(t), f(t), v(t), q(t)$$
        Parameters:
        $$\epsilon, \tau_s, \tau_f, \alpha, \tau_0, E_0, V_0$$
        Constants:
        $$a_1, a_2$$
        Input:
        $$u(t)$$
  \end{column}
  \end{columns}
  \note{System is dissipative:\\
  If no input is provided, it will rather quickly decay.\\
  Constant input leads to steady state response.\\
  First term in $\dot{q}$ is the metabolism term.\\
  Outflow is the $v^{1/\alpha}$ term\\
  Significant nonlinearity.\\
  $a_1 = (4.3\nu_0TE+\epsilon_025\epsilon_0)E_0$, $a_2 = \epsilon_025\epsilon_0E_0 + .43$}
\end{frame}

@@

\section{Particle Filter}
%frame with example

\begin{frame}{Construction}
\begin{itemize}
    \item Mixture PDF:\\
        $$\alpha(X) \stackrel{\text{\tiny{k=0}}}{\approx} P(x_k) 
                = \sum_{i=0}^{N_p} w^i\delta(x_k - x^i_k ) dx$$
    \item Particle Weights at time $t_k$:\\
        $$w^i_k \propto \frac{P(x^i_{0:k} | y_{0:k})}{q(x^i_{0:k} | y_{0:k})}$$
      \note{$q$ is the density/location of the particle}
      \note{$p$ is the actual probability }
    \item Adding Measurements:\\
        $$w^i_k \propto & w^i_{k-1}P(y_k| x_k) $$
      \note{Because of the proportion, note that the weights do not
            have to integrate to 1, and can be extremely large or extremely small}
\end{itemize}
\end{frame}
